\TheTitle

### 2017-07-09 paper/design.tex
Linvis design and implementation

@@

\begin{itemize}
        \item Filter by searching
        \item View files edited
        \item View modules
        \item Tree viewer
\end{itemize}

\subsection{Searching}

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/search.png}
        \caption{Search View allows filtering commits that were merged in a given
                period, filtering by author, keyword, or commit ID.}
        \label{fig:search}
\end{figure}

Searching (depicted in Figure \ref{fig:search}) allows a user to filter
commits and merges that are irrelevant. The search mechanism breaks down
the results by release version. A user can further narrow down the
search by specifying a range of dates in which such commits were merged
by Linus into the master branch---not when the commits were created
(author date and/or commit date). This distinction is important. We have
observed commits that have taken years to arrive into the master
repository after they were originally created.

A user may then provide a search text, filtering by the author name, the
commit ID, or keyword from the log. Any part of the author name may show
up in the results, including searching by email address.

If the user is searching by commit ID, the ID can be specified by using
any of its unique prefixes. For example, the commit
\mycode{3f17ea6dea8ba5668873afa54628a91aaa3fb1c0} is returned when the
user searches for a commit ID of \mycode{3f17e} in the 3.16 Linux
kernel.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/search_results_2.png}
        \caption{Search Results. Each table entry is a commit merged in the desired
                merged window.}
        \label{fig:results}
\end{figure}

In the search results (seen in Figure~\ref{fig:results}), the user is
presented with the one-line log message preview, the author's name and
email, the date the commit was authored, and the date the commit was
last committed.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/log_view.png}
        \caption{Panel showing the Commit Message of a commit.}
        \label{fig:message}
\end{figure}

Once a user selects a commit or merge to investigate, they are presented
with a tabbed pane allowing them to view the full commit log, the files
edited, the modules involved, and the merge-tree view.

The first tab displays the full commit log (Figure~\ref{fig:message}).
From this, a user is able to see what they would see had they searched
for the commit using Git log. This doesn't provide additional
information to the other tools, but helps to complete the functionality
of \tool. The commit log provides a user with the information about the
content of the commit and who has signed-off on the commit to ensure
that it is of good quality. The message for merges may contain a summary
of the commits being merged.  The information within these messages is
highly variable, and is completely dependent on the author's style. As
the user moves toward the root-level merge, the quality of these
messages generally improves.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/files_view_2.png}
        \caption{Panel showing the files modified by all the commits that are part
                of this merge.}
        \label{fig:files}
\end{figure}

The second tab is the files tab (Figure~\ref{fig:files}). This tab
provides information on what files have been edited, how many lines were
added, and how many lines were removed in a given commit. For
non-merges, this functionality is similar to the other tools available.
Our tree-based design model allows us to extend this functionality to
merges by aggregating information about all the commits that are
children of the merge in the merge-tree, which other tools are unable to
show. To find the number of lines added to a file in a merge, we take
the sum of the lines added to that file in each of the children of that
merge. We do the same for calculating the number of lines removed.

% This could be extended to use the patch information to determine when a line has been
% replaced rather than incrementing the lines added and removed.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/modules_view_2.png}
        \caption{Panel showing the modules changed by all the commits in this merge.}
        \label{fig:modules}
\end{figure}

The modules tab (Figure~\ref{fig:modules}) shows the modules that are
contained within the commit. Modules are not natively recognized by Git,
and are not going to be present in all repositories. In the Linux
repository, authors put the module they are working on in the one-line
summary of the log-message; for example: the log \emph{gcov: add support
  for FCC 4.9} has updated the \emph{gcov} module (the coverage testing
tool of the kernel). We heuristically extract the module by taking all
text in the log summary of commits until the first colon.  Modules are
logical partitions of the information in the kernel. Depending on where
the author was working, modules can be general, such as ``bluetooth''
and ``wireless'', or can be quite specific for individual hardware, such
as ``ath9k\_hw'' and ``wl1251''. In a few cases, the author of a commit
does not correctly follow this format and the heuristic approach fails.
As with the Files panel, non-merge commits show their corresponding
information, but for merge commits we aggregate all the modules changed
in all the commits that are part of that merge.  The output of this view
is shown in Figure~\ref{fig:modules}.

Finally, we have the Tree view tab. The tree view is designed for
providing easy navigation of the commits within the merge-tree that is
rooted in the current merge.  It also provides a clear topological view
of the merge and the submerges it includes. We have experimented with
various tree designs to find a design that allows for easy navigation
and visualization of both large and small trees. We discuss this panel
in the next subsection.

\subsection{Merge-Tree Views} \label{treeview_section}

The merge-tree view is what makes \tool unique to other tools that
inspect the DAG of a Git repository. With it, a user can inspect how
commits are merged on their way to the master branch. We have
experimented with various types of trees:

\begin{enumerate}
        \item List trees are a text-based representation of the merge-tree, and are easy to search and navigate.
        \item Reingold-Tilford trees provide a clear visual representation of the tree structure of the merge-tree.
        \item Bubble trees organize the data hierarchically by having the parent node contain the child nodes similarly to tree maps, but
                clearly showing the parent-child relationships between commits and merges.
\end{enumerate}

@@

The list tree viewer (Figure~\ref{fig:list_tree}) is in the form of
nested lists, and is designed to more closely model the tree view found
in file browsers. This tree only contains the commits and merges that
are within the subtrees of the current merge. A commit will never have
any items in this tree as it is a leaf. To accompany the tree, we
include breadcrumbs at the top of the page to enable a user to navigate
both from the root to the leaves and from a leaf to the root. The last
item in the breadcrumb list is the current commit, the previous item is
the parent of the current commit, and the first item is the root merge
into the kernel.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/list_tree.png}
        \caption{List tree view of merge 3f17ea6}
        \label{fig:list_tree}
\end{figure}

\subsubsection{Reingold-Tilford Tree}

The Reingold-Tilford tree\cite{Reingold1981} (Figures
\ref{fig:reingold_tree} and \ref{fig:reingold_tree_zoom}) allows the
visualization and navigation of the entire merge-tree in an intuitive
representation of the tree.  This illustrates a clear notion of root and
leaves, and how to navigate in either direction. Some merge trees are
very large, containing thousands of commits and merged. While the tree
is capable of producing a visualization, it becomes far more difficult
to understand. For example, the merge, 3f17ea6 performed by Linus
Torvalds June 8 2014, contains 7217 commits and merges. \footnote{This
  commit can be inspected at
  \url{http://li.turingmachine/org/commits/3f17ea6dea8ba5668873afa54628a91aaa3fb1c0}}

      \begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/4dc4_tree.pdf}
        \caption{Merge 4dc4226 is a subtree of 3f17ea6, for the power-management
          module of the kernel}
        \label{fig:reingold_tree}
      \end{figure}

      \begin{figure*}
        \centering
        \includegraphics[width=0.98\textwidth]{figures/4dc4_zoom_tree.pdf}
        \caption{Zoomed out view of the Reingold-Tilford tree for merge 4dc4226}
        \label{fig:reingold_tree_zoom}
      \end{figure*}

      The user is initially greeted with their current node centered on
      the screen.  They are able to zoom the tree by scrolling the
      mouse, and clicking and dragging to pan the tree. They can see
      more details about a node by clicking on it, which will provide
      them a link to the specific page for that commit.

\subsubsection{Bubble Tree}

Bubble trees are useful for providing a clear visualization of wide,
hierarchical data\cite{Boardman2000}. The tree structure is represented
by the nesting of nodes; the largest circle is the root, containing all
the other nodes. The smallest circles do not contain any nodes and
therefore represent the leaf nodes.

Our implementation of the bubble tree (Figure~\ref{fig:bubble_tree})
provides the user with a clear picture of where a commit is located in
the merge tree. We highlight the selected commit or merge in red.
Non-selected merges are in a shade of blue determined by the depth of a
node in the tree. The root is the lightest shade of blue, while the
contained merges are progressively darker; the commits are white.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/bubble_tree.pdf}
        \caption{Bubble Tree of merge 3f17ea6, merge 4dc4226 is the currently
          selected merge and is highlighted in orange.}
        \label{fig:bubble_tree}
\end{figure}

The bubble tree doesn't have an implicit way of providing additional
information, placing any text near the nodes makes the tree impossible
to read, so we include a separate pane in the web page. When a user
hovers over a node, the pane shows additional information about the
author and the commit message and a link to the detailed page for that
commit or merge. If the user clicks on a node, the tree will zoom to
that node and the information in the info pane will persist, enabling
the user to click the link. This tree provides an easy mechanism for
users to navigate from the root to the leaves and vice versa.

>>>>

We constructed a web-based tool called \tool in order to navigate and
inspect the \mt model of the kernel. Creating the web-based tool enables
users to use the system without having to install additional software or
store a large database, which makes it more accessible, easily
maintainable, and platform independent.

@@

\begin{itemize}
        \item Filter by searching
        \item View aggregated summaries of authors, files, and modules
        \item Visualize \mt{s}
\end{itemize}

\subsection{Search}

\tool provides a search engine for navigating within the kernel,
filtering commits that are not relevant. The search engine takes a
plain text query from the user and returns the results that are relevant
in the order of relevancy. When computing relevancy, the engine uses the
commit log, the author name, the filenames, the commit hash, the date
the commit was authored, and the date the commit was committed.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=\linewidth]{figures/linvis/search_results.png}
  \caption{A single merge tree in the search results of \tool, showing
    the link to the root at the top and a table of the relevant commits
    in the bottom, sorted by relevance.}
  \label{fig:search_results}
\end{figure}

Before presentation, the results are grouped by merge tree. Each
merge tree group has a link to the root-node of the tree at the top,
followed by a table of commits and merges within the tree that match the
query, shown in Figure~\ref{fig:search_results}. The table includes the
relevancy rank of the entry, the commit log message preview, author, the
date the repository event was committed, and the date it was authored.
The merge tree groups are ordered based on the mean of the relevancy
scores of the relevant results in that tree.

\subsection{Summarization}
\label{sub:summarization}

\tool uses seven tabs to show the information and visualizations for a
selected commit or merge. The message tab shows the full commit log
message. This does not include the diff, but given the commit hash, this
information can be found directly from the repository. The files tab
shows an aggregated table of all files that were modified in a merge. It
includes metrics like the number of lines added, lines removed, total
lines modified, and the delta, summed across all commits in the merge
tree that modify this file. A details drop-down button allows a user to
see exactly which commit makes the changes, as shown in
Figure~\ref{fig:linvis_files}. If the current repository event being
viewed is a commit, the aggregate views will only show modifications
made by the commit. The modules tab shows the modules modified in the
merge tree. Like the files tab, the modules tab uses a table to show the
name of the module, the number of commits that are in the merge tree
that work with the module, and a details button to provide the links to
those commits.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=\linewidth]{figures/linvis/linvis_files.png}
  \caption{Table showing the modified files in a merge, with the second
  entry expanded to show the commit that makes the changes.}
  \label{fig:linvis_files}
\end{figure}

The authorship tab is very similar to the files tab, but shows the
authorship information. It shows the sum of the number of lines added,
removed, modified, and the delta within the \mt. It also shows
the number of files that were modified by the author. The details tab is
organized slightly differently. Instead of organizing these results by
commit, the details are organized by file, showing which files were
modified by the author in this \mt (Figure~\ref{fig:linvis_authors}).

\begin{figure}[htpb]
  \centering
  \includegraphics[width=\linewidth]{figures/linvis/linvis_authors.png}
  \caption{Table showing the authors who made changes in a merge. The
    entry for Randy Dunlap is expanded, showing the modifications to
    each file that were made by Randy.}
  \label{fig:linvis_authors}
\end{figure}

\subsection{Visualization}
\label{sub:visualization}

The ability to easily visualize the integration of commits into a
project is what makes \tool unique from other tools. \tool implements
three visualizations, the list tree, pack tree, and \rt tree.

@@

The list tree, depicted in Figure~\ref{fig:linvis_list_tree}, is
constructed as a series of nested lists. The nesting indicates the
parent-child relationship. This visualization is text-based enabling
fast navigation to commits using the built-in search fin most
web-browsers. The list tree is rooted at the current repository event;
if the current event being inspected is a commit, only that commit will
be shown. Conversely, if the selected event is the root, the entire
merge tree will be shown.

\begin{figure}
        \centering
        \includegraphics[width=0.9\linewidth]{figures/linvis/linvis_list_tree.png}
        \caption{The list tree visualization}
        \label{fig:linvis_list_tree}
\end{figure}

\subsubsection{\rt Tree}

The \rt tree\cite{Reingold1981}, depicted for two trees in
Figure~\ref{fig:study_commits}, is the classic tree visualization, with
the root at the top, leaves at the bottom, and edges between them
showing the parent-child relationship. This tree visualization works
very well in many cases, but does not easily visualize very wide trees,
with many repository events on a single level.

When a user first looks at the visualization, the current repository
event is placed in the center. Furthermore, it is highlighted in bright
orange. Commits, the leaves, are shown in white, while the merges are
colored shades of blue where lighter blue indicates fewer child events
of that node, and darker blue indicates more children.

\subsubsection{Pack Tree}

Pack trees\cite{Wang2006} are useful for displaying an overview of large
data sets. The initial goals for the pack tree were for visualizing file
systems, which are similar to git repositories in that they are
relatively shallow, but very wide trees. The tree is represented by sets
of nested circles. The largest circle, containing all of the other
nodes, is the root, while the smallest circles are the leaves. In our
representation, the root maps to the merge into the master branch, while
the leaves are the commits.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/linvis/linvis_bubble.pdf}
  \caption{The pack tree visualization, with the root depicted as the
    outer-most circle, containing all other nodes, the leaves depicted
    as white circles containing no other nodes. The currently selected
    event is shown in orange.}
  \label{fig:linvis_pack}
\end{figure}

We depict the pack tree in Figure~\ref{fig:linvis_pack}. Like with the
\rt tree, \tool uses white to indicate the individual commits, and
orange to indicate the currently selected node. The inner merges are
colored with shades of blue to indicate the depth in the tree. Darker
shades of blue indicate that the merge is deeper in the tree.
